Awareness and Experience of Developers to\\ Outdated and License-incompatible Code on Stack Overflow:\\ An Online Survey

### 2017-11-04 cloverflow_technical_report/cloverflow_survey_rn.tex
Completed the overall discussion and added Baltes et al. study to the Related Work.

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
upvotes for good questions and useful answers. \FIXME{I don't understand the
	sentence. @Jens Ok now?:} For example, they gain reputation when they receives a vote up for
their question (+5), a vote up for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

@@

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels. The first channel is via the first
author's social media post (Facebook) inviting software developers who have
experience of copying code snippets from Stack Overflow to take the survey. The
second channel is a popular technology news and media community in Thailand
called \textsf{blognone.com} which attracts a high number of Thai software
developers. The first author posted an invitation to the visitor survey in a
discussion forum mentioning the requirements to take the survey. The third
channel collected answers from the University of Molise with the help of an
external researcher. The last two channels are the
\textsf{comp.lang.java.programmer} group and the Software Engineering
Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

@@

We asked the visitors whether they have had any problem from reusing Stack Overflow
code snippets and how often did the problems occur.  Fifty seven (out of eighty
seven) participants (see Figure~\ref{fig:survey_v_problems}) experienced a
problem from reusing Stack Overflow snippets. Among the 57, there are 2
participants who found problems in more than 80\% of the reused code snippets.
Eight and sixteen faced problems from at least sixty and forty percent of the
reused snippets.

@@

\subsubsection{Stack Overflow Answerers}
By separating the answerers into two groups, we are able to compare the answers and
observe similarities or differences in their answers according to their reputation. In summary, we found the
following.

The sources of code snippets in Stack Overflow answers are similar in both
groups. The answerers mainly write the code snippets from scratch aiming to
answer the question. Considering the frequencies of copying from each source,
i.e.~personal projects, company projects, open source projects, writing from
scartch, modifying from the questions, and others, they also follow the same
proportion for both group.

The answerers in Group 1 have larger percentage (61.2\%) of being notified about
outdated code in their answers than Group 2 (47.1\%). Nevertheless, since
Group-1 answerers have higher reputation than Group-2 answerers, they
potentially have given more answers on Stack Overflow than Group 2. The higher amount of
answers may increase the chance of the code being outdated. Nevertheless, while the number of being notified of
outdated code is lower, the percentage of the answerers in Group 2 who very
frequently fixed their outdated code are higher than of Group 1.

Regarding software license, the answerers in both groups show the same level of
awareness to Stack Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly,
the answerers in both groups neither include software license in their code
snippets (98\% and 99\%) nor check of license compatibility between their
code snippet's and Stack Overflow CC BY-SA 3.0 (69\%).

@@

Another research area is knowledge extraction from Stack Overflow.
\cite{Nasehi2012}~studied what makes a good code example by analysing answers
from Stack Overflow. Similarly, \cite{Yang2016} report the number of reusable
code snippets on Stack Overflow across various programming languages.
\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic
modelling to analyse questions and answers from Stack Overflow so that they can
automatically categorise new questions. There are also studies trying to
understand developers' behaviours on Stack Overflow, e.g.~A study by
\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
\cite{Yang2017} analysed 909k non-fork Python projects on GitHub and 1.9 million
python code snippets on Stack Overflow and found thousands of code blocks that
are copied from Stack Overflow to GitHub.

>>>>

\subsubsection{The answerer survey} 
We selected the participants for our answerer survey based on their Stack
Overflow reputations. On Stack Overflow, a user's reputation reflects how much
the community trusts the user. A user earns reputation when he or she receives
upvotes for good questions and useful answers. \FIXME{I don't understand the
	sentence. @Jens Ok now?:} For example, they gain reputation when they receives an upvote for
their question (+5), an upvote for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

@@

\subsubsection{The visitor survey} 
We adopted non-probability convenient sampling to invite participants for this
survey. Participation in the survey requires experience of visiting Stack
Overflow for solving programming tasks at least once. The participants were
invited to take the survey via five channels. The first channel is via the first
author's social media post (Facebook) inviting software developers who have
experience of copying code snippets from Stack Overflow to take the survey. The
second channel is a popular technology news and media community in Thailand
called \textsf{blognone.com} which attracts a high number of Thai software
developers. The first author posted an invitation to the visitor survey in a
discussion forum mentioning the requirements to take the survey. The third
channel collected answers from the University of Molise in Italy, where the third author
works. The last two channels are the
\textsf{comp.lang.java.programmer} group and the Software Engineering
Facebook page. The number of participants taken the survey is shown in
Table~\ref{tab:visitors}.

@@

We asked the visitors whether they have had any problem from reusing Stack Overflow
code snippets and how often did the problems occur.  Fifty seven out of eighty
seven participants (66\%) experienced a
problem from reusing Stack Overflow snippets (see Figure~\ref{fig:survey_v_problems}). Among the 57, there are 2
participants who found problems in more than 80\% of the reused code snippets.
Eight and sixteen faced problems from at least sixty and forty percent of the
reused snippets.

@@

By separating the answerers into two groups according to their reputation, we
observed some similarities and differences in their responses. The sources of
code snippets in Stack Overflow answers are similar in both groups. The
answerers mainly write the code snippets from scratch aiming to answer the
question. The frequencies of copying from each source, i.e.~personal projects,
company projects, open source projects, writing from scratch, modifying from the
questions, and others, also follow the same proportions for both group.

The main difference we found is responses regarding outdated code. The answerers
in Group 1 have a more substantial percentage (61.2\%) of being notified about
the outdated code in their answers than Group 2 (47.1\%). This may be caused by
the amount of their Stack Overflow answers. Since Group-1 answerers have a
higher reputation than Group-2 answerers, they possibly have given more answers
on Stack Overflow. The higher amount of answers hence increase the chance of the
code being outdated. Interestingly, although the percentage of outdated code
notifications in Group 2 is lower, the percentage of the answerers who very
frequently fixed their outdated code is higher than of Group 1.

Regarding software license, the responses from the two groups agree with each
other. The answerers in both groups show the same level of awareness to Stack
Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly, the answerers in
both groups neither include software license in their code snippets (98\% and
99\%) nor check of license compatibility between their code snippet's and Stack
Overflow CC BY-SA 3.0 (69\%).

The visitors survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\citep{Acar2016,An2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never reports back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. We also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

Another research area is knowledge extraction from Stack Overflow.
\cite{Nasehi2012}~studied what makes a good code example by analysing answers
from Stack Overflow. Similarly, \cite{Yang2016} report the number of reusable
code snippets on Stack Overflow across various programming languages.
\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic
modelling to analyse questions and answers from Stack Overflow so that they can
automatically categorise new questions. There are also studies trying to
understand developers' behaviours on Stack Overflow, e.g.~A study by
\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
\cite{Yang2017} analysed 909k non-fork Python projects on GitHub and 1.9 million
python code snippets on Stack Overflow and found thousands of code blocks that
are copied from Stack Overflow to GitHub. \cite{Baltes2017} discovered that two
third of the clones from 10 most frequently referenced Java code snippets on Stack
Overflow do not contain attributions.
